### 2019-06-04 doc/chapters/trying_verify_checktx.tex
added foot note

According to the Bitcoin protocol this is possible.
A transaction can have multiple outputs that should be referenceable by the next transaction.
What should not be possible is a transaction referencing the same output twice.
This was a bug in Bitcoin Core known as CVE-2018–17144 which was patched on September 18, 2018.

Here, Bitcoin-S did a bit too much and marked all transaction as invalid, if they referenced a transaction twice in the next transaction.
The fix is, to check on TransactionOutPoint instead of TransactionOutPoint.txId, because TransactionOutPoint contains the txId as well as the output index it references.
\begin{lstlisting}[language=scala]
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}
Since TransactionOutPoint is a case class and Scala has a built in == for case classes there is no need to implement TransactionOutPoint.==.
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.396]{images/bitcoin-s-pr.png}
	\caption{Line changes for PR \#435 from GitHub}
	\label{fig:output1}
\end{figure}

This was fixed in pull request \mypound435 on GitHub at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.

>>>>

According to the Bitcoin protocol this is possible.
A transaction can have multiple outputs that should be referenceable by the next transaction.
What should not be possible is a transaction referencing the same output twice.
This was a bug in Bitcoin Core known as CVE-2018–17144 which was patched on September 18, 2018. \cite{cve201817144}

Here, Bitcoin-S did a bit too much and marked all transaction as invalid, if they referenced a transaction twice in the next transaction.
The fix is, to check on TransactionOutPoint instead of TransactionOutPoint.txId, because TransactionOutPoint contains the txId as well as the output index it references.
\begin{lstlisting}[language=scala]
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}

Since TransactionOutPoint is a case class and Scala has a built in == for case classes there is no need to implement TransactionOutPoint.==.
\begin{figure}[H]
	\centering
		\includegraphics[scale=0.396]{images/bitcoin-s-pr.png}
	\caption{Line changes for PR \#435 from GitHub}
	\label{fig:output1}
\end{figure}

This was fixed in pull request \mypound435 on GitHub\footnote{https://github.com/bitcoin-s/bitcoin-s/pull/435} at April 23, 2019 by us along a unit test to prevent this bug from appearing again in the future.
